\Rpackage{MSnbase} input/output capabilities

### 2012-08-14 inst/doc/MSnbase-development/MSnbase-development.Rnw
readMgfData update and new MSnbase-io vignette
 o in readMgfData, SCANS is not used to populate 
   acquisitionNum anymore, as several scans might 
   have been combined upstreams <2011-09-26 Mon>
 o added fillUp function in utils.R and exported <2011-09-27 Tue>
 o new MSnbase-io vignette <2011-09-28 Wed>




git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@58519 bc3139a8-67e5-0310-9ffc-ced21a209358
using knitr instead of pgfSweave and misc vignette updated
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@68442 bc3139a8-67e5-0310-9f

\SweaveOpts{echo=T,eval=T,fig=F,results=verbatim,cache=F,tikz=T,external=T,prefix.string=sweave-cache/figs/fig}

\newcommand{\R}{\texttt{R} }
\newcommand{\Rfunction}[1]{{\texttt{#1}}}
\newcommand{\Robject}[1]{{\texttt{#1}}}
\newcommand{\Rpackage}[1]{{\textit{#1}}}
\newcommand{\email}[1]{\href{mailto:#1}{\normalfont\texttt{#1}}}
%% colors
\definecolor{Red}{rgb}{0.7,0,0}
\definecolor{Blue}{rgb}{0,0,0.8}

\hypersetup{%
  hyperindex = {true},
  colorlinks = {true},
  linktocpage = {true},
  plainpages = {false},
  linkcolor = {Blue},
  citecolor = {Blue},
  urlcolor = {Red},
  pdfstartview = {Fit},
  pdfpagemode = {UseOutlines},
  pdfview = {XYZ null null null}
}

@@

@@

%% <<setup,cache=FALSE>>=
%% setCacheDir("sweave-cache/values")
%% @

<<environment,cache=FALSE,echo=FALSE>>=
library(MSnbase)
@

@@

Raw data is currently imported from \texttt{mzXML} files \citep{Pedrioli2004} <
using the \Rfunction{xcms:::rampRawData} 
and \Rfunction{xcms:::rampRawDataMSn} functions from the 
\Rpackage{xcms} package \citep{Smith2006}.
These functions do not give access to the meta data. New importer functions are 
under development (see for instance \Rpackage{mzR}\footnote{%%
  \url{https://github.com/sneumann/mzR/blob/master/DESCRIPTION}}) that will 
hopefully give programmatic access to meta data stored in the data file to 
populate the \Robject{MIAPE} object.

@@

The choices of attributes has been dictated by the \Rfunction{xcms:::rampRawData} 
and \Rfunction{xcms:::rampRawDataMSn} functions and what data from the 
\texttt{mzXML} file they gave access to. 
It is expected that some hopefully minor changes might 
come up here when migrating to other data import packages, that allow random access 
to \texttt{mzXML} data and support \texttt{mzML} \citep{Martens2010}.

@@

<<Spectrum>>=
getClass("Spectrum1")
@

<<Spectrum>>=
getClass("Spectrum2")
@

@@

<<ReporterIons>>=
getClass("NAnnotatedDataFrame")
@

@@

\input{NoteAboutSpeedAndMemory.tex}

@@

<<label=sessioninfo,results=tex,echo=FALSE,cache=FALSE>>=
toLatex(sessionInfo())
@

>>>>

\newcommand{\R}{\texttt{R} }
\newcommand{\Rfunction}[1]{{\texttt{#1}}}
\newcommand{\Robject}[1]{{\texttt{#1}}}
\newcommand{\Rpackage}[1]{{\mbox{\normalfont\textsf{#1}}}}
\newcommand{\email}[1]{\href{mailto:#1}{\normalfont\texttt{#1}}}
%% colors
\definecolor{Red}{rgb}{0.7,0,0}
\definecolor{Blue}{rgb}{0,0,0.8}

\usepackage{geometry}
\geometry{verbose,
  tmargin = 2.5cm,
  bmargin = 2.5cm,
  lmargin = 3.5cm,
  rmargin = 3.5cm}

\usepackage{hyperref}
\usepackage{breakurl}
\hypersetup{%
  pdfusetitle,
  bookmarks = {true},
  bookmarksnumbered = {true},
  bookmarksopen = {true},
  bookmarksopenlevel = 2,
  unicode = {true},
  breaklinks = {false},
  hyperindex = {true},
  colorlinks = {true},
  linktocpage = {true},
  plainpages = {false},
  linkcolor = {Blue},
  citecolor = {Blue},
  urlcolor = {Red},
  pdfstartview = {Fit},
  pdfpagemode = {UseOutlines},
  pdfview = {XYZ null null null}
}

@@

<<'setup', include = FALSE, cache = FALSE>>=
library(knitr)
opts_chunk$set(fig.align = 'center', 
               fig.show = 'hold', 
               par = TRUE,
               prompt = FALSE,
               comment = NA)
options(replace.assign = TRUE, 
        width = 65)
knit_hooks$set(par = function(before, options, envir) {
  if (before && options$fig.show != 'none') 
    par(mar = c(4,4,.1,.1),
        cex.lab = .95,
        cex.axis = .9,
        mgp = c(2,.7,0),
        tcl = -.3)
})
@

@@

<<environment, cache=FALSE, echo=FALSE>>=
suppressPackageStartupMessages(library(MSnbase))
@

@@

%% Raw data is currently imported from \texttt{mzXML} files \citep{Pedrioli2004} <
%% using the \Rfunction{xcms:::rampRawData} 
%% and \Rfunction{xcms:::rampRawDataMSn} functions from the 
%% \Rpackage{xcms} package \citep{Smith2006}.
%% These functions do not give access to the meta data. New importer functions are 
%% under development (see for instance \Rpackage{mzR}\footnote{%%
%%   \url{https://github.com/sneumann/mzR/blob/master/DESCRIPTION}}) that will 
%% hopefully give programmatic access to meta data stored in the data file to 
%% populate the \Robject{MIAPE} object.

@@

%% The choices of attributes has been dictated by the \Rfunction{xcms:::rampRawData} 
%% and \Rfunction{xcms:::rampRawDataMSn} functions and what data from the 
%% \texttt{mzXML} file they gave access to. 
%% It is expected that some hopefully minor changes might 
%% come up here when migrating to other data import packages, that allow random access 
%% to \texttt{mzXML} data and support \texttt{mzML} \citep{Martens2010}.

@@

<<Spectrum1>>=
getClass("Spectrum1")
@

<<Spectrum2>>=
getClass("Spectrum2")
@

@@

<<NAnnotatedDF>>=
getClass("NAnnotatedDataFrame")
@

@@

%% \input{NoteAboutSpeedAndMemory.tex}

@@

<<label=sessioninfo, results=tex, echo=FALSE, cache=FALSE>>=
toLatex(sessionInfo())
@

### 2012-08-14 inst/doc/MSnbase-io/MSnbase-io.Rnw
using knitr instead of pgfSweave and misc vignette updated
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@68442 bc3139a8-67e5-0310-9ffc-ced21a209358

\SweaveOpts{echo=T,eval=T,fig=F,results=verbatim,cache=F,tikz=T,external=T,prefix.string=sweave-cache/figs/fig}

@@

\hypersetup{%
  hyperindex = {true},
  colorlinks = {true},
  linktocpage = {true},
  plainpages = {false},
  linkcolor = {Blue},
  citecolor = {Blue},
  urlcolor = {Red},
  pdfstartview = {Fit},
  pdfpagemode = {UseOutlines},
  pdfview = {XYZ null null null}
}

@@

%% pgf settup
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}
% Define block styles
\tikzstyle{input} = [rectangle, draw, fill=blue!20,
  text width=6em, text centered, rounded corners, minimum height=4em]
\tikzstyle{fun} = [rectangle, draw, fill=white, drop shadow, 
  text width=7em, text centered, rounded corners, minimum height=2em]
\tikzstyle{obj} = [rectangle, draw, fill=red!20, 
  text width=5em, text centered, rounded corners, minimum height=5em]

@@

%% <<setup,cache=FALSE>>=
%% setCacheDir("sweave-cache/values")
%% @

%% <<environment,cache=FALSE,echo=FALSE>>=
%% library(MSnbase)
%% @

@@

>>>>

@@

\usepackage{geometry}
\geometry{verbose,
  tmargin = 2.5cm,
  bmargin = 2.5cm,
  lmargin = 3.0cm,
  rmargin = 3.0cm}

\usepackage{hyperref}
\usepackage{breakurl}
\hypersetup{%
  pdfusetitle,
  bookmarks = {true},
  bookmarksnumbered = {true},
  bookmarksopen = {true},
  bookmarksopenlevel = 2,
  unicode = {true},
  breaklinks = {false},
  hyperindex = {true},
  colorlinks = {true},
  linktocpage = {true},
  plainpages = {false},
  linkcolor = {Blue},
  citecolor = {Blue},
  urlcolor = {Red},
  pdfstartview = {Fit},
  pdfpagemode = {UseOutlines},
  pdfview = {XYZ null null null}
}

%% pgf setup
\pgfdeclarelayer{background}
\pgfdeclarelayer{foreground}
\pgfsetlayers{background,main,foreground}
% Define block styles
\tikzstyle{input} = [rectangle, draw, fill=blue!20,
  text width=6em, text centered, rounded corners, minimum height=4em]
\tikzstyle{fun} = [rectangle, draw, fill=white, drop shadow, 
  text width=7em, text centered, rounded corners, minimum height=2em]
\tikzstyle{obj} = [rectangle, draw, fill=red!20, 
  text width=5em, text centered, rounded corners, minimum height=5em]

@@

@@

\vspace{10mm}

<<knitr, include=FALSE, cache=FALSE>>=
library(knitr)
opts_chunk$set(fig.align = 'center', 
               fig.show = 'hold', 
               par = TRUE,
               prompt = TRUE,
               comment = NA)
options(replace.assign = TRUE, 
        width = 70)
knit_hooks$set(par = function(before, options, envir) {
  if (before && options$fig.show != 'none') 
    par(mar = c(4,4,.1,.1),
        cex.lab = .95,
        cex.axis = .9,
        mgp = c(2,.7,0),
        tcl = -.3)
})
@

@@

\clearpage
